---
title: "dmfail_slidy"
author: "Vvsy"
date: "1/16/2019"
output:
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#predict dmfail

## logistic regression 
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_regreg.Rda"
load(file)
results_regreg
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_regreg.Rda"
load(file)
cfm_regreg
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_regreg.Rda"
load(file)
roc_regreg
```

## logistic rigid 
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_rigid.Rda"
load(file)
results_rigid
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_rigid.Rda"
load(file)
cfm_rigid
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_rigid.Rda"
load(file)
roc_rigid
```

## logistic lasso
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_lasso.Rda"
load(file)
results_lasso
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_lasso.Rda"
load(file)
cfm_lasso
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_lasso.Rda"
load(file)
roc_lasso
```

## logistic GAM
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_GAM.Rda"
load(file)
results_GAM
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_GAM.Rda"
load(file)
cfm_GAM
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_GAM.Rda"
load(file)
roc_GAM
```

## Decision Tree
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_dtree.Rda"
load(file)
results_dtree
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_dtree.Rda"
load(file)
cfm_dtree
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_dtree.Rda"
load(file)
roc_dtree
```

## k-Nearest Neighbor 
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_knn.Rda"
load(file)
results_knn
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_knn.Rda"
load(file)
cfm_knn
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_knn.Rda"
load(file)
roc_knn
```

## Random Forest
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_rf.Rda"
load(file)
results_rf
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_rf.Rda"
load(file)
cfm_rf
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_rf.Rda"
load(file)
roc_rf
```

## Neural Networks
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_nnet.Rda"
load(file)
results_nnet
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_nnet.Rda"
load(file)
cfm_nnet
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_nnet.Rda"
load(file)
roc_nnet
```

## Bagging
### train result
```{r}
file="/Users/wongshnyau/Desktop/results_bagg.Rda"
load(file)
results_bagg
```
### confusion matrix
```{r}
file="/Users/wongshnyau/Desktop/cfm_bagg.Rda"
load(file)
cfm_bagg
```
### roc
```{r}
file="/Users/wongshnyau/Desktop/roc_bagg.Rda"
load(file)
roc_bagg
```

## select model
### compare model 
```{r}
table <- matrix(c(0.6865,0.7231,0.6833,0.7231,0.6349,0.5,0.7188,0.7588,0.7176,0.7034,0.6816,0.6989,0.9053,0.9589,0.6457,0.6505,0.9091,0.9536),ncol=2,byrow=TRUE)
colnames(table) <- c("Accuracy","ROC")
rownames(table) <- c("logistic","logistic rigid","logistic lasso","logistic GAM","DT","K-NN","RF","NN","Bagging")
table <- as.table(table)
table
```
### best model
  - 擁有最好準確率的模型為Bagging，準確率為0.9091，ROC CURVE為0.9536，接著我們使用它來預測答案。
  
